SI

### 2021-02-26 ms/si.Rmd
Add 2012 time subplots to SI DT chamber figure

```{r si-load-data, cache = FALSE}
tar_load(filmy_dt_chamber)
tar_load(filmy_dt)
tar_load(filmy_habit)
tar_load(rel_water_indiv)
tar_load(rel_water_species_means)
tar_load(filmy_phy)
tar_load(filmy_habit)
tar_load(range_comparison)
tar_load(light_data_all)
tar_load(light_models)
tar_load(filmy_lc_model_params)
tar_load(filmy_lc_model_fitted_data)
tar_load(combined_species_means)
tar_load(gameto_indiv_times)
```

```{r si-load-functions, cache = FALSE}
# Define functions specific to this file
plot_chamber_rh <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = 0.01*rh)) +
    geom_line(size = 0.25) +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = label_percent(accuracy = 1)) +
    labs(y = "Relative humidity") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank())
}

plot_chamber_temp <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = temp)) +
    geom_line(size = 0.25) +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = label_number(suffix = "\u00b0C", accuracy = 1)) +
    labs(y = "Temperature") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank())
}

plot_sporo_chamber_time <- function (data, time_limits) {
  ggplot(data, aes(x = species, ymin = pre, ymax = post, y = post, group = species_duration, linetype = dry_time)) +
    geom_linerange(position = position_dodge(0.5)) +
    geom_point(position = position_dodge(0.5)) +
    scale_y_datetime(limits = time_limits) +
    scale_x_discrete(labels = str_abbrev_sp_pretty) +
    scale_linetype_manual(values = c("15" = "solid", "2" = "solid")) +
    coord_flip() +
    labs(x = "Species") +
    theme(
      axis.title = element_blank(),
      axis.text.y = element_markdown(),
      legend.position = "none"
    )
}

@@

```{r sporophyte-dt-LiCl, fig.height = 6.5, fig.width = 9, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
licl_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "LiCl", 3)
licl_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "LiCl", 1)

licl_clusters <- bind_rows(licl_clusters_2013, licl_clusters_2014)

@@

licl_time_range_2012 <- c(min = min(licl_chamber_data_2012$date_time), max = max(licl_chamber_data_2012$date_time))

@@

# Temp plots
licl_temp_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = temp, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = licl_time_range_2014) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = licl_temp_range) +
  labs(
    y = "Temperature",
    title = "2014") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    legend.position = "none") +
  blank_x_theme()

@@

licl_temp_plot_2012 <- plot_chamber_temp(licl_chamber_data_2012, licl_time_range_2012) +
  scale_y_continuous(limits = licl_temp_range) +
  labs(title = "2012") +
  theme(plot.title = element_text(hjust = 0.5, size = 11)) +
  blank_y_theme() +
  blank_x_theme()

# RH plots
licl_rh_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = 0.01*rh, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = licl_time_range_2014) +
  scale_y_continuous(
    label = label_percent(accuracy = 1), 
    limits = licl_rh_range) +
  labs(y = "Relative humidity") +
  theme(legend.position = "none") +
  blank_x_theme()

@@

licl_rh_plot_2012 <- plot_chamber_rh(licl_chamber_data_2012, licl_time_range_2012) +
  scale_y_continuous(limits = licl_rh_range, label = label_percent(accuracy = 1)) +
  blank_y_theme()

# Dry times plot
licl_time_plot_2013 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2013) +
  blank_y_theme()
licl_time_plot_2014 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2014)

# Combine plots
licl_temp_plot_2014 + licl_temp_plot_2013 + licl_temp_plot_2012 +
  licl_rh_plot_2014 + licl_rh_plot_2013 + licl_rh_plot_2012 +
  licl_time_plot_2014 + licl_time_plot_2013 + plot_spacer() +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "a") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

mgno3_clusters <- bind_rows(mgno3_clusters_2013, mgno3_clusters_2014)

@@

mgno3_time_range_2012 <- c(min = min(mgno3_chamber_data_2012$date_time), max = max(mgno3_chamber_data_2012$date_time))

@@

# Temp plots
mgno3_temp_plot_2014 <- ggplot(mgno3_chamber_data_2014, aes(x = date_time, y = temp, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = mgno3_time_range_2014) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = mgno3_temp_range) +
  labs(
    y = "Temperature",
    title = "2014") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    legend.position = "none") +
  blank_x_theme()

@@

mgno3_temp_plot_2012 <- plot_chamber_temp(mgno3_chamber_data_2012, mgno3_time_range_2012) +
  scale_y_continuous(limits = mgno3_temp_range) +
  labs(title = "2012") +
  theme(plot.title = element_text(hjust = 0.5, size = 11)) +
  blank_y_theme() +
  blank_x_theme()

# RH plots
mgno3_rh_plot_2014 <- ggplot(mgno3_chamber_data_2014, aes(x = date_time, y = 0.01*rh, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = mgno3_time_range_2014) +
  scale_y_continuous(
    label = label_percent(accuracy = 1), 
    limits = mgno3_rh_range) +
  labs(y = "Relative humidity") +
  theme(legend.position = "none") +
  blank_x_theme()

@@

mgno3_rh_plot_2012 <- plot_chamber_rh(mgno3_chamber_data_2012, mgno3_time_range_2012) +
  scale_y_continuous(limits = mgno3_rh_range, label = label_percent(accuracy = 1)) +
  blank_y_theme()

# Dry times plot
mgno3_time_plot_2013 <- plot_sporo_chamber_time(mgno3_clusters, mgno3_time_range_2013) +
  blank_y_theme()
mgno3_time_plot_2014 <- plot_sporo_chamber_time(mgno3_clusters, mgno3_time_range_2014)

# Combine plots
mgno3_temp_plot_2014 + mgno3_temp_plot_2013 + mgno3_temp_plot_2012 +
  mgno3_rh_plot_2014 + mgno3_rh_plot_2013 + mgno3_rh_plot_2012 +
  mgno3_time_plot_2014 + mgno3_time_plot_2013 + plot_spacer() +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "b") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

>>>>

```{r si-load-data, cache = FALSE}
tar_load(filmy_dt_chamber)
tar_load(filmy_dt)
tar_load(filmy_habit)
tar_load(rel_water_indiv)
tar_load(rel_water_species_means)
tar_load(filmy_phy)
tar_load(filmy_habit)
tar_load(range_comparison)
tar_load(light_data_all)
tar_load(light_models)
tar_load(filmy_lc_model_params)
tar_load(filmy_lc_model_fitted_data)
tar_load(combined_species_means)
tar_load(gameto_indiv_times)
tar_load(sporo_dt_times)
```

```{r si-load-functions, cache = FALSE}
# Define functions specific to this file
plot_chamber_rh <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = 0.01*rh)) +
    geom_line(size = 0.25) +
    scale_x_datetime(limits = time_limits, minor_breaks = "1 day") +
    scale_y_continuous(label = label_percent(accuracy = 1)) +
    labs(y = "Relative humidity") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank())
}

plot_chamber_temp <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = temp)) +
    geom_line(size = 0.25) +
    scale_x_datetime(limits = time_limits, minor_breaks = "1 day") +
    scale_y_continuous(label = label_number(suffix = "\u00b0C", accuracy = 1)) +
    labs(y = "Temperature") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank())
}

plot_sporo_chamber_time <- function (data, time_limits) {
  ggplot(data, aes(x = species, ymin = pre, ymax = post, y = post, group = species_duration, linetype = dry_time)) +
    geom_linerange(position = position_dodge(0.5)) +
    geom_point(position = position_dodge(0.5)) +
    scale_y_datetime(limits = time_limits, minor_breaks = "1 day") +
    scale_x_discrete(labels = str_abbrev_sp_pretty) +
    scale_linetype_manual(values = c("15" = "solid", "2" = "solid")) +
    coord_flip() +
    labs(x = "Species") +
    theme(
      axis.title = element_blank(),
      axis.text.y = element_markdown(),
      legend.position = "none"
    )
}

@@

```{r change-theme-1}
previous_theme <- theme_set(theme_bw(base_size = 10))
```

```{r sporophyte-dt-LiCl, fig.height = 6.6, fig.width = 9, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
licl_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "LiCl", 3)
licl_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "LiCl", 1)

licl_clusters <- bind_rows(licl_clusters_2013, licl_clusters_2014) %>%
  bind_rows(filter(sporo_dt_times, salt == "LiCl")) %>%
  mutate(species_duration = paste(species, dry_time))

@@

licl_time_range_2012 <- c(
  # Manually entered data for sporo dt times LiCl was slightly earlier than 
  # when started datalogger recording
  min = filter(sporo_dt_times, salt == "LiCl") %>% pull(pre) %>% min, 
  max = max(licl_chamber_data_2012$date_time)
  )

@@

# Temp plots
licl_temp_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = temp, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = licl_time_range_2014) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = licl_temp_range) +
  labs(
    y = "Temperature",
    title = "2014") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    legend.position = "none") +
  blank_y_theme() +
  blank_x_theme()

@@

licl_temp_plot_2012 <- plot_chamber_temp(licl_chamber_data_2012, licl_time_range_2012) +
  scale_y_continuous(limits = licl_temp_range) +
  labs(title = "2012") +
  theme(plot.title = element_text(hjust = 0.5, size = 11)) +
  blank_x_theme()

# RH plots
licl_rh_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = 0.01*rh, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = licl_time_range_2014) +
  scale_y_continuous(
    label = label_percent(accuracy = 1), 
    limits = licl_rh_range) +
  labs(y = "Relative humidity") +
  theme(legend.position = "none") +
  blank_x_theme() +
  blank_y_theme()

@@

licl_rh_plot_2012 <- plot_chamber_rh(licl_chamber_data_2012, licl_time_range_2012) +
  scale_y_continuous(limits = licl_rh_range, label = label_percent(accuracy = 1)) +
  blank_x_theme()

# Dry times plot
licl_time_plot_2012 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2012) 
licl_time_plot_2013 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2013) +
  blank_y_theme()
licl_time_plot_2014 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2014) +
  blank_y_theme()

# Combine plots
licl_temp_plot_2012 + licl_temp_plot_2013 + licl_temp_plot_2014 +
  licl_rh_plot_2012 + licl_rh_plot_2013 + licl_rh_plot_2014 +
  licl_time_plot_2012 + licl_time_plot_2013 + licl_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "a") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

mgno3_clusters <- bind_rows(mgno3_clusters_2013, mgno3_clusters_2014) %>%
  bind_rows(filter(sporo_dt_times, salt == "MgNO3")) %>%
  mutate(species_duration = paste(species, dry_time))

@@

mgno3_time_range_2012 <- c(
  # Manually entered data for sporo dt times LiCl was slightly earlier than 
  # when started datalogger recording
  min = filter(sporo_dt_times, salt == "MgNO3") %>% pull(pre) %>% min, 
  max = max(mgno3_chamber_data_2012$date_time)
  )

@@

# Temp plots
mgno3_temp_plot_2014 <- ggplot(mgno3_chamber_data_2014, aes(x = date_time, y = temp, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = mgno3_time_range_2014) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = mgno3_temp_range) +
  labs(
    y = "Temperature",
    title = "2014") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    legend.position = "none") +
  blank_x_theme() +
  blank_y_theme()

@@

mgno3_temp_plot_2012 <- plot_chamber_temp(mgno3_chamber_data_2012, mgno3_time_range_2012) +
  scale_y_continuous(limits = mgno3_temp_range) +
  labs(title = "2012") +
  theme(plot.title = element_text(hjust = 0.5, size = 11)) +
  blank_x_theme()

# RH plots
mgno3_rh_plot_2014 <- ggplot(mgno3_chamber_data_2014, aes(x = date_time, y = 0.01*rh, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = mgno3_time_range_2014, minor_breaks = "1 day") +
  scale_y_continuous(
    label = label_percent(accuracy = 1), 
    limits = mgno3_rh_range) +
  labs(y = "Relative humidity") +
  theme(legend.position = "none") +
  blank_y_theme() +
  blank_x_theme()

@@

mgno3_rh_plot_2012 <- plot_chamber_rh(mgno3_chamber_data_2012, mgno3_time_range_2012) +
  scale_y_continuous(limits = mgno3_rh_range, label = label_percent(accuracy = 1)) +
  blank_x_theme()

# Dry times plot
mgno3_time_plot_2012 <- plot_sporo_chamber_time(mgno3_clusters, mgno3_time_range_2012)
mgno3_time_plot_2013 <- plot_sporo_chamber_time(mgno3_clusters, mgno3_time_range_2013) +
  blank_y_theme()
mgno3_time_plot_2014 <- plot_sporo_chamber_time(mgno3_clusters, mgno3_time_range_2014) +
  blank_y_theme()

# Combine plots
mgno3_temp_plot_2012 + mgno3_temp_plot_2013 + mgno3_temp_plot_2014 +
  mgno3_rh_plot_2012 + mgno3_rh_plot_2013 + mgno3_rh_plot_2014 +
  mgno3_time_plot_2012 + mgno3_time_plot_2013 + mgno3_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "b") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

```{r change-theme-2}
theme_set(previous_theme)
```
